Comparison of FDR methods on GWAS with SummarizedBenchmark

### 2017-10-25 datasets/GWAS/GWAS-SummarizedBenchmark.Rmd
Add results plots (overlap and nrejects)

```{r, GWAS1-plot, results="hide", width=15, height=12}
# plot adjusted p-values by effect_size (diagnostic from ASH paper)
plotsim_single(data.frame(assay(sb)), bmi, strat = "effect_size")

>>>>

```{r, GWAS1-plot, results="hide", width=15, height=15}
# plot adjusted p-values by effect_size (diagnostic from ASH paper)
plotsim_single(data.frame(assay(sb)), bmi, strat = "effect_size")
